\documentclass[11pt]{article}

% ---------------------------------------------------------------------------
% Packages
% ---------------------------------------------------------------------------
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
% A scalable outline font is required: microtype's font expansion cannot
% operate on the default Computer Modern bitmaps, and pdfTeX aborts with
% "auto expansion is only possible with scalable fonts". If your distribution
% provides Latin Modern, `\usepackage{lmodern}' preserves the classic Computer
% Modern appearance; the URW fonts below are used here because they ship with
% every TeX installation, including minimal ones.
\usepackage{mathptmx}   % Times for text and mathematics
\usepackage[scaled=0.9]{helvet}  % Helvetica for sans-serif
\usepackage{courier}    % Courier for monospace
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{listings}
\usepackage[margin=1in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{siunitx}
\usepackage{authblk}
\usepackage{microtype}
% Long \texttt{} strings such as file paths and package names cannot hyphenate
% and would otherwise overflow the margin. Permitting breaks after common
% separators keeps them inside the text block.
\usepackage[htt]{hyphenat}

\sisetup{
  detect-all,
  separate-uncertainty = true,
  range-units = single
}

% Listing style for the code excerpts.
\definecolor{codebg}{RGB}{248,249,250}
\definecolor{codekw}{RGB}{0,92,197}
\definecolor{codecm}{RGB}{106,115,125}
\definecolor{codestr}{RGB}{3,47,98}

\lstdefinelanguage{JavaScriptES6}{
  keywords={import, from, export, const, let, function, return, await, async,
            if, else, for, of, new, class, extends, throw, try, catch},
  keywordstyle=\color{codekw}\bfseries,
  ndkeywords={true, false, null, undefined, NaN, Infinity},
  ndkeywordstyle=\color{codekw},
  comment=[l]{//},
  morecomment=[s]{/*}{*/},
  commentstyle=\color{codecm}\itshape,
  stringstyle=\color{codestr},
  morestring=[b]',
  morestring=[b]",
  morestring=[b]`,
  sensitive=true
}

\lstset{
  language=JavaScriptES6,
  backgroundcolor=\color{codebg},
  basicstyle=\ttfamily\footnotesize,
  breaklines=true,
  captionpos=b,
  frame=single,
  framesep=4pt,
  rulecolor=\color{gray!30},
  showstringspaces=false,
  xleftmargin=6pt,
  xrightmargin=6pt
}

% ---------------------------------------------------------------------------
% Title
% ---------------------------------------------------------------------------
\title{\bfseries STEMKit: A Client-Side Web Architecture for Secure,
Reproducible Computational Chemistry and Data Analysis Workflows}

\author[1]{Olanrewaju M. Daramola\thanks{ORCID: \href{https://orcid.org/0009-0006-3327-2047}{0009-0006-3327-2047}}}
\affil[1]{Independent Researcher}

\date{\today}

\begin{document}

\maketitle

% ---------------------------------------------------------------------------
\begin{abstract}
\noindent
Computational chemistry generates a steady stream of small analytical tasks
that fall between the major simulation packages: reading a GROMACS
\texttt{.xvg} file to check convergence, converting coordinates between
\si{\nano\metre} and \si{\angstrom}, computing a centre of mass, testing
whether two sets of replicates differ, or composing a scheduler script that
requests appropriate resources. Each is individually simple, yet collectively
they impose enough friction --- an environment to configure, a dependency to
install, a script to relocate --- that they are frequently performed manually
and therefore inconsistently. The available remedies each carry a cost: local
Python tooling demands an environment that managed institutional machines
often disallow; web services require uploading data, which is unacceptable for
unpublished results or material under confidentiality agreement; and graphical
desktop applications resist scripting and hence reproduction.

We present STEMKit, a suite of 21 browser-based tools built on
\texttt{@stemkit/core}, a JavaScript library of parsing and numerical routines
carrying no dependency on the document object model. All computation executes
within the user's browser using the \texttt{FileReader} API; no data is
transmitted, no account is required, and no installation is performed. Because
all computation runs locally in the browser, no user data reaches an external
server. The same modules also execute under Node.js, so an analysis explored
interactively can be captured as a script, version-pinned, and placed under
continuous integration without rewriting.

The library comprises 15 domain modules validated by 975 automated tests. Numerical
results are verified against independent references --- SciPy for inferential
statistics, NumPy for regression, \texttt{scipy.constants} for each
conversion factor, and physical invariants for structural geometry --- rather
than against the implementation itself. Extraction of the computational core
from the original monolithic scripts exposed three numerical defects that had
propagated into reported output, each of which is documented, corrected, and
covered by regression tests.
\end{abstract}

\vspace{1em}
\noindent\textbf{Keywords:} computational chemistry, molecular dynamics,
GROMACS, PLUMED, client-side computation, data privacy, reproducibility,
open-source software

% ---------------------------------------------------------------------------
\section{Introduction}
\label{sec:introduction}

The software landscape of computational chemistry is well served at its
extremes. Simulation engines such as GROMACS~\cite{abraham2015} and
LAMMPS~\cite{thompson2022} are mature, extensively validated, and actively
maintained; analysis frameworks such as MDAnalysis~\cite{michaudagrawal2011}
provide comprehensive programmatic access to trajectory data. Between these
poles lies a substantial volume of routine work that neither category serves
comfortably.

Consider the interval between completing a simulation and reporting it. A
researcher must inspect the RMSD to confirm equilibration, extract a radius of
gyration, convert a structure between the nanometre convention of GROMACS and
the \si{\angstrom} convention of the Protein Data Bank, compare replicate
measurements statistically, digitise a figure from a paper for comparison,
abbreviate journal titles in a reference list, and compose a scheduler script
requesting an appropriate resource allocation. None of these operations is
intellectually demanding. All of them are error-prone when performed by hand,
and all of them are performed repeatedly.

\subsection{The friction problem}

Three classes of solution exist, and each imposes a characteristic cost.

\paragraph{Local scripting.} A Python environment with MDAnalysis, NumPy, and
SciPy addresses every task listed above and is the correct instrument for
sustained analytical work. Its cost is environmental. Managed institutional
workstations frequently prohibit package installation; conda environments
drift; and a script written six months ago may no longer execute against the
current interpreter. For a researcher whose primary expertise lies in
chemistry rather than software engineering, this cost is not negligible.

\paragraph{Web services.} Server-side tools eliminate installation entirely but
require data transmission. For unpublished results, material subject to a
confidentiality agreement, or work under embargo, this is frequently
prohibited outright. Even where permitted, the transfer creates a record whose
retention policy the researcher does not control.

\paragraph{Desktop applications.} Graphical applications avoid both problems
but introduce a third: they are difficult to script. An analysis performed by
clicking cannot readily be re-executed, version-controlled, or subjected to
continuous integration. In practice such an analysis is difficult to reproduce,
even when every step was recorded at the time.

\subsection{The client-side position}

Modern browsers provide a capable computational environment. The
\texttt{FileReader} API grants access to local files without transmission;
JavaScript engines execute numerical code fast enough for the data volumes
involved. ECMAScript modules make it possible to organise that code properly,
instead of accumulating scripts.

We built STEMKit around these constraints. No server participates in the
computation, so there is nothing to which data could be transmitted; users do
not have to take a privacy policy on trust. Its reproducibility property derives from a separate architectural
decision --- the numerical core is extracted into modules with no dependency on
the browser, so the identical code that executes behind the interface also
executes under Node.js.

This paper describes that architecture, the workflows it supports, the
numerical methods underlying each computation, and the defects that the
extraction process exposed in the original implementation.

% ---------------------------------------------------------------------------
\section{Software Architecture}
\label{sec:architecture}

\subsection{Separation of computation from presentation}

The original implementation followed the pattern common to browser tooling:
each of the 21 tools consisted of an HTML document paired with a single
JavaScript file combining event handling, rendering, and computation. This
arrangement is expedient during development and progressively obstructive
thereafter. Computational logic entangled with DOM manipulation cannot be
tested without a browser, cannot be reused across tools, and cannot be invoked
from a script.

The refactoring applied the \emph{strangler fig} pattern: for each tool, the
mathematical and parsing logic was extracted into a pure module beneath
\texttt{src/core/}, a test suite was written against the extracted module, and
the original file was then reduced to DOM wiring that imports the new
functions. The user-visible interface is unchanged; the computation beneath it
is now independently addressable.

Table~\ref{tab:modules} enumerates the resulting modules.

\begin{table}[htbp]
\centering
\caption{Modules of \texttt{@stemkit/core}. Vendored dependencies are supplied
by injection (Section~\ref{sec:injection}); modules marked \emph{none} operate
without any third-party code.}
\label{tab:modules}
\small
\begin{tabular}{@{}llrl@{}}
\toprule
\textbf{Module} & \textbf{Domain} & \textbf{Tests} & \textbf{Dependency} \\
\midrule
\texttt{bibtex} & Reference deduplication, sanitising & 89 & bibtex-parse-js \\
\texttt{statistics} & Inferential statistics & 82 & jStat \\
\texttt{structure} & Molecular geometry, PDB/GRO/XYZ & 79 & none \\
\texttt{xvg-parser} & GROMACS/PLUMED trajectory data & 77 & none \\
\texttt{curve-fitting} & Least-squares regression & 72 & regression.js \\
\texttt{plumed} & PLUMED input generation & 72 & none \\
\texttt{selection} & Atom selection, spatial queries & 67 & none \\
\texttt{slurm} & HPC job-script generation & 61 & none \\
\texttt{latex} & Table generation and escaping & 59 & none \\
\texttt{error-bars} & Group summaries, error bars & 57 & jStat \\
\texttt{units} & Physical unit conversion & 56 & none \\
\texttt{journals} & Journal title abbreviation & 53 & none \\
\texttt{data-cleaning} & Tabular transformation & 51 & Papa Parse \\
\texttt{outliers} & Anomaly detection & 51 & jStat \\
\texttt{digitizer} & Figure digitisation & 49 & none \\
\midrule
\textbf{Total}         &                                 & \textbf{975} & \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Dependency injection across execution environments}
\label{sec:injection}

Four third-party libraries are vendored within the repository: jStat for
statistical distributions, Papa Parse for delimited-text parsing,
regression.js for curve fitting, and bibtex-parse-js for reference parsing.
Each is distributed as a Universal Module Definition (UMD) bundle, which
detects its host at run time and either assigns \texttt{module.exports} under
CommonJS or attaches a global to \texttt{window} in a browser.

Neither path is reachable from a plain ECMAScript module. A UMD file contains
no \texttt{export} statements, so a direct import yields no bindings; and
\texttt{import \{ createRequire \} from 'module'} --- the conventional Node.js
workaround --- constitutes a hard \emph{resolution} failure in a browser, which
occurs before any code executes and therefore cannot be intercepted by
\texttt{try}/\texttt{catch}.

Rather than branch on the execution environment inside every module, which
would render the core untestable in one of its two targets, the library
declares the libraries it requires and each host registers them at
initialisation:

\begin{lstlisting}[caption={Registration under Node.js and in the browser.}]
// Node.js: the vendored bundles are loaded through createRequire.
import { createRequire } from 'module';
import { registerVendor } from '@stemkit/core';

const require = createRequire(import.meta.url);
registerVendor({ jStat: require('./js/dependencies/jstat.min.js') });

// Browser: the UMD <script> tags have already installed their globals.
import { registerFromGlobals } from './src/core/index.js';
registerFromGlobals();
\end{lstlisting}

Modules request their dependencies lazily, at the point of use rather than at
import time, so that importing any module never fails merely because an
unrelated library has not yet been registered. The result is a single code
path shared by both environments, with the vendored libraries remaining the
sole source of truth for the numerics in each.

One consequence merits explicit note, as it is a common failure mode. A
repository declaring \texttt{"type": "module"} instructs Node.js to parse every
\texttt{.js} file beneath it as an ECMAScript module, including the vendored
UMD bundles. Under that interpretation the UMD factory takes its browser
branch and fails. Scoping \texttt{"type": "commonjs"} to the dependency
directory alone restores correct behaviour.

\subsection{Testing strategy}

The suite comprises 975 tests across the 15 domain modules. Its governing principle is
that numerical results are validated against \emph{independent} references
rather than against the implementation under test, since a test written from
the same source as the code confirms only internal consistency.

Reference values were obtained from SciPy~\cite{virtanen2020} for t-tests,
ANOVA, correlation, non-parametric tests, quantiles, and multiple-comparison
correction; from NumPy~\cite{harris2020} for regression coefficients and
descriptive statistics; from \texttt{scipy.constants} for every unit conversion
factor; and from physical invariants for structural geometry --- specifically
the molecular weight and centre of mass of water, the orthonormality of
rotation matrices, the preservation of interatomic distances under rotation,
and round-trip fidelity through every supported file format.

An end-to-end smoke test additionally exercises one representative path through
each module against a real installation, detecting the class of failure that
unit tests cannot: a broken aggregate export, a misconfigured module type
declaration, or a vendored bundle that fails to load.

% ---------------------------------------------------------------------------
\section{Workflows}
\label{sec:workflows}

\subsection{Molecular dynamics trajectory analysis}

GROMACS writes analysis output in the Grace format, a plain-text convention in
which lines beginning with \texttt{\#} are comments, lines beginning with
\texttt{@} are formatting directives, and all remaining non-empty lines are
whitespace-delimited numeric records. The directives carry the plot title, axis
labels, and per-series legends. Discarding them --- as a naive parser that
skips all non-numeric lines would --- loses precisely the metadata that
identifies which column contains which observable.

% AUTHOR: add one concrete example here -- the system and trajectory you
% actually inspected while building this (e.g. "a 200 ns simulation of X in
% explicit solvent, ~90k atoms"). A named real system is the single most
% convincing detail in this section, and it must be one of yours.
The \texttt{xvg-parser} module recovers this metadata alongside the numeric
matrix:

\begin{lstlisting}[caption={Parsing a GROMACS RMSD trajectory.}]
import { parseXvg, extractColumn, columnStats } from '@stemkit/core';
import { readFileSync } from 'fs';

const { matrix, headers, title } = parseXvg(readFileSync('rmsd.xvg', 'utf8'));
// title   -> "RMSD & Radius of Gyration"
// headers -> ["Time (ps)", "Backbone RMSD", "Rg"]

headers.slice(1).forEach((name, i) => {
  const s = columnStats(extractColumn(matrix, i + 1));
  console.log(`${name}: ${s.mean.toFixed(4)} +/- ${s.std.toFixed(4)} nm`);
});
\end{lstlisting}

Malformed records are counted and reported, not silently discarded, so a
truncated trajectory is visible to the user instead of quietly shortening the
analysis. Two further details of the format are handled explicitly. The Grace
multi-set separator \texttt{\&} is treated as a delimiter, not parsed as data.
Records containing \texttt{NaN} or \texttt{Infinity} are rejected whole; one
non-finite entry would otherwise contaminate every downstream statistic.

\subsection{PLUMED collective-variable output}

PLUMED~\cite{tribello2014} writes \texttt{COLVAR} files whose header lines
begin with \texttt{\#!} and carry field names and metadata. Although the
convention differs from Grace, the comment character coincides, and the same
parser therefore handles both formats without modification --- the header lines
are skipped as comments and the numeric records parsed identically. This is
verified by an explicit test rather than left to assumption.

\subsection{Structure files and molecular geometry}

The \texttt{structure} module parses the three coordinate formats in routine
use for classical simulation: PDB and GROMACS \texttt{.gro}, both fixed-column
formats in which fields are located by character position, and XYZ, which is
whitespace-delimited. Fixed-column parsing is essential rather than pedantic: a
residue name may legitimately be blank, and a whitespace-splitting parser would
silently shift every subsequent field on such a line.

Unit handling is explicit throughout. PDB and XYZ express coordinates in
\si{\angstrom}; \texttt{.gro} uses \si{\nano\metre}. Every parse result carries
its unit, and conversion is always deliberate. Silently mixing the two is the
single most direct route to a structure that is wrong by a factor of ten.

\subsubsection{Element inference from atom names}

Assigning an element to each atom is a prerequisite for any mass-weighted
quantity, and PDB atom names are ambiguous by construction. The name
\texttt{CA} denotes the $\alpha$-carbon in a protein residue and calcium in an
ion record. The resolution implemented here proceeds in five stages:

\begin{enumerate}
  \item An explicit element column, where present, takes priority.
  \item A leading digit is a hydrogen-count prefix (\texttt{1HB},
        \texttt{2HG1}) and is stripped before the symbol is read.
  \item An unambiguous two-letter metal (\texttt{FE}, \texttt{ZN},
        \texttt{SE}) is recognised wherever it appears, including within a host
        residue such as haem or selenomethionine.
  \item Otherwise, a two-letter prefix whose second character is uppercase is a
        PDB remoteness indicator, and only the first letter is the element:
        \texttt{CA} in a protein residue is C$\alpha$.
  \item As a final fallback, a two-letter symbol is trusted when the residue
        shares its name, the convention for monatomic ions.
\end{enumerate}

% AUTHOR: if you noticed this on a specific structure -- a PDB code, a
% metalloprotein you work on -- name it. That is the detail a reviewer will
% believe came from the bench rather than from a code review.
Stages 2 and 3 correct defects present in the original implementation, which
assigned fluorine to haem iron, sulfur to selenomethionine selenium, and no
element at all to numeric-prefixed hydrogens. The resolution is validated
against 40 atom names drawn from real structures, covering protein backbone and
side-chain atoms, nucleic acid atoms, water, monatomic ions, and metal centres.

\subsubsection{Geometric quantities}

The module computes the geometric centroid, the mass-weighted centre of mass,
the axis-aligned bounding box, and the radius of gyration
\begin{equation}
  R_g = \sqrt{\frac{\sum_i m_i \left| \mathbf{r}_i - \mathbf{R} \right|^2}
                   {\sum_i m_i}},
  \qquad
  \mathbf{R} = \frac{\sum_i m_i \mathbf{r}_i}{\sum_i m_i},
\end{equation}
together with rigid-body rotation about an arbitrary pivot using intrinsic
$Z$--$Y$--$X$ Euler angles. Velocities present in a \texttt{.gro} file rotate
with the frame but are never translated, so that a round trip through rotation
and export preserves the kinetic state.

\subsection{HPC job-script generation}

Composing a scheduler script correctly requires knowledge that is
engine-specific and easily misapplied. Two aspects dominate the resulting waste
of allocation.

First, the resource model differs by engine. GROMACS is threaded and requires
one MPI rank per node with many CPUs per task; LAMMPS is MPI-parallel and
requires many ranks per node. Emitting the wrong shape either idles most of a
node or oversubscribes it.

% AUTHOR: if this bit you on a real cluster, say so and name it. One sentence
% of the form "on our institutional cluster this silently queued N jobs" is
% worth more than the general statement below.
Second, and less widely appreciated, the SLURM \texttt{-{}-mem} directive in an
array job specifies memory \emph{per task}, not per job. A request of
\SI{32}{\giga\byte} across a hundred-task array asks the scheduler for
\SI{3.2}{\tera\byte} concurrently. The generator computes the true in-flight
total and reports it:

\begin{lstlisting}[caption={Generating a GROMACS submission script.}]
import { generateScript } from '@stemkit/core';

const { script, warnings } = generateScript({
  engine: 'gromacs', jobName: 'prod_md', partition: 'gpu',
  nodes: 1, gpus: 1, cpusPerTask: 16,
  walltime: '24:00:00', memory: '32G',
  modules: ['gcc/11.3', 'cuda/12.1', 'gromacs/2023.3'],
  tpr: 'md.tpr', deffnm: 'md', maxh: 23.5
});

warnings.forEach(w => console.warn(`[${w.level}] ${w.message}`));
\end{lstlisting}

Generated scripts include checkpoint-resume logic, so that a requeued job
continues from its last checkpoint rather than silently restarting from
$t = 0$ --- a failure mode that consumes an entire allocation while appearing
to succeed. Warnings are returned as structured objects rather than formatted
strings, leaving presentation to the caller.

\subsection{Figure digitisation}

Recovering numerical values from a published figure requires a two-point affine
calibration per axis. On a logarithmic axis the interpolation must be performed
in logarithmic space,
\begin{equation}
  v(p) = 10^{\,\log_{10} v_1
              + \dfrac{(p - p_1)\left(\log_{10} v_2 - \log_{10} v_1\right)}
                      {p_2 - p_1}},
\end{equation}
because a decade occupies a constant pixel distance there. Treating a
logarithmic axis linearly is the most frequent source of error in figure
digitisation, and it produces values that are plausible rather than obviously
wrong.

The module additionally reports the data-space uncertainty corresponding to a
one-pixel positioning error. Stating this alongside digitised values is honest
practice: the precision of a digitised point is determined by the resolution of
the figure, not by the number of decimal places the export happens to print.

\subsection{Unit conversion}

Sixty-four units across ten categories are supported, each defined by its
ratio to a category base unit. Conversion therefore reduces to
\begin{equation}
  x_{\mathrm{to}} = x_{\mathrm{from}}
    \cdot \frac{f_{\mathrm{to}}}{f_{\mathrm{from}}},
\end{equation}
which keeps the table linear in the number of units rather than quadratic and
renders every entry independently checkable against its cited source.
Conversion factors are CODATA 2018 values~\cite{tiesinga2021}; each was
verified against \texttt{scipy.constants} during testing. Temperature is
handled separately, since the Celsius and Fahrenheit scales are affine rather
than multiplicative and cannot be expressed by a single factor.

% ---------------------------------------------------------------------------
\section{Statistical Rigour}
\label{sec:statistics}

\subsection{Test selection and assumption checking}

The statistical module implements Welch's~\cite{welch1947} and Student's
t-tests, the paired t-test, one-way ANOVA, Pearson correlation, the
Mann--Whitney $U$ test, and the Wilcoxon signed-rank test. Welch's test is the
default for independent samples, as it does not assume equal variances and
loses negligible power when they are in fact equal.

Every parametric test reports an effect size and, where standard, a confidence
interval. Assumptions are checked and surfaced rather than presumed: normality
by the D'Agostino--Pearson $K^2$ omnibus test~\cite{dagostino1971}, and
homogeneity of variance by the median-centred Brown--Forsythe variant of
Levene's test~\cite{brown1974}, chosen for its markedly greater robustness to
non-normality than the original mean-centred formulation. Where an assumption
fails, a non-parametric alternative is recommended.

\subsection{Numerical methods}

Table~\ref{tab:methods} maps each computed quantity to its numerical method and
validation reference.

\begin{table}[htbp]
\centering
\caption{Numerical methods and validation references.}
\label{tab:methods}
\small
\begin{tabular}{@{}p{3.9cm}p{5.2cm}p{4.8cm}@{}}
\toprule
\textbf{Quantity} & \textbf{Method} & \textbf{Validated against} \\
\midrule
Student / Welch $t$, $p$ &
  Regularised incomplete beta $I_x(a,b)$ &
  \texttt{scipy.stats.ttest\_ind} \\
Welch--Satterthwaite $\nu$ &
  Closed form &
  SciPy, hand calculation \\
One-way ANOVA $F$, $p$ &
  Sum-of-squares decomposition; $I_x$ tail &
  \texttt{scipy.stats.f\_oneway} \\
Pearson $r$, CI &
  Fisher $z$ transform &
  \texttt{scipy.stats.pearsonr} \\
Mann--Whitney $U$ &
  Tie-corrected normal approximation &
  \texttt{scipy.stats.mannwhitneyu} \\
Wilcoxon $W$ &
  Signed-rank, zeros discarded &
  \texttt{scipy.stats.wilcoxon} \\
D'Agostino--Pearson $K^2$ &
  Skewness and kurtosis transforms &
  \texttt{scipy.stats.normaltest} \\
Levene $W$ &
  Brown--Forsythe (median-centred) &
  \texttt{scipy.stats.levene} \\
Quantiles &
  Linear interpolation (type 7) &
  \texttt{numpy.percentile} \\
Multiple comparisons &
  Holm--Bonferroni~\cite{holm1979} &
  Independent implementation \\
Grubbs $G$ &
  Inverted $t$ critical value &
  \texttt{scipy.stats.t.ppf} \\
Modified $Z$-score &
  Median/MAD, $0.6745$ scaling~\cite{iglewicz1993} &
  \texttt{numpy} \\
Least-squares fitting &
  Normal equations (regression.js) &
  \texttt{numpy.polyfit} \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Cancellation in tail probabilities}

Upper-tail probabilities are computed through the complementary form of the
incomplete beta and gamma functions rather than as $1 - F(x)$. The two
expressions are algebraically identical; numerically they are not. Once $F(x)$
rounds to unity in double precision, the subtraction cancels completely and the
result is exactly zero.

The consequence is not academic. For the one-way ANOVA used in our test suite
($F = 377.545$ on $2$ and $21$ degrees of freedom), the naive form returns
$p = 0$, whereas
\begin{equation}
  p = I_{\frac{d_2}{d_2 + d_1 F}}\!\left(\tfrac{d_2}{2}, \tfrac{d_1}{2}\right)
    = \num{3.4611747382914e-17},
\end{equation}
agreeing with SciPy to twelve significant figures. A continuous test statistic
cannot produce $p = 0$. When that value appears in published output it indicates
a numerical fault in the software, not an unusually strong effect.

The same treatment is applied to the Student $t$, $\chi^2$, and normal tails.
Beyond $|z| \approx 8$ the vendored \texttt{erfc} implementation underflows, and
a documented asymptotic expansion takes over so that a $p$-value is reported as
\num{1.5e-23} rather than as zero.

\subsection{Defects exposed by extraction}

Separating computation from presentation subjected the numerical code to
independent verification for the first time. Three defects were identified that
had propagated into reported output.

\paragraph{Standardised moments.} Skewness and kurtosis are defined against the
\emph{population} standard deviation,
\begin{equation}
  G_1 = \frac{\sqrt{n(n-1)}}{n-2}
        \cdot \frac{1}{n}\sum_{i=1}^{n}
        \left(\frac{x_i - \bar{x}}{\sigma_{\mathrm{pop}}}\right)^{\!3},
  \qquad
  \sigma_{\mathrm{pop}} = \sqrt{\frac{1}{n}\sum_i (x_i - \bar{x})^2}.
\end{equation}
The original implementation used the Bessel-corrected sample standard
deviation, deflating skewness by a factor of $\left((n-1)/n\right)^{3/2}$ ---
approximately \SI{15}{\percent} at $n = 10$. Because both moments feed the
D'Agostino--Pearson statistic, every normality $p$-value the tool reported was
affected.

\paragraph{Tail underflow.} As described above, all upper-tail probabilities
were computed by subtraction and floored at zero for strong effects.

\paragraph{Element misassignment.} Haem iron was assigned the mass of fluorine
(\SI{18.998}{\dalton} rather than \SI{55.845}{\dalton}), selenomethionine
selenium the mass of sulfur, and numeric-prefixed hydrogens no mass at all.
Molecular weights and centres of mass computed for metalloproteins were
correspondingly wrong.

Each defect is corrected and covered by a regression test. Users who generated
figures with earlier versions of these tools should re-check any reported
skewness, normality $p$-value, or metalloprotein mass.

\subsection{An inherited limitation}

We have not fixed one limitation, only documented it. The vendored
regression.js library fits exponential, power, and logarithmic models by
\emph{linearisation}:
taking logarithms and performing least squares in the transformed space,
additionally weighting the fit by $y$. This minimises error in logarithmic
space rather than in the original units and is therefore not the
maximum-likelihood fit under additive Gaussian noise.

The magnitude is material. For a clean doubling series the library returns a
growth rate of $\num{0.69022}$ where unweighted logarithmic least squares gives
$\ln 2 = \num{0.69315}$. Neither value is incorrect --- they answer different
questions --- but the difference is large enough to matter when a rate constant
is reported. The \texttt{fitCurve} function exposes a \texttt{linearised} flag
so that callers may surface the distinction, and users requiring
publication-grade non-linear fits are directed to Levenberg--Marquardt
optimisation on untransformed data.

% ---------------------------------------------------------------------------
\section{Availability and Reproducibility}
\label{sec:availability}

STEMKit is released under the MIT licence. The browser tools require no
installation; the library is obtained by cloning the repository and running
\texttt{npm install}.

The complete test suite executes with \texttt{npm test}, and an end-to-end
smoke test with \texttt{node tests/smoke.mjs}. Both are intended to be run by
users evaluating the software, not solely by its maintainers: a library whose
numerical claims cannot be checked by its users offers reproducibility only in
principle.

Each tool that generates a figure also emits a standalone matplotlib script
reproducing that figure from the original data file. This closes the loop
between interactive exploration and reproducible output: a plot examined in the
browser can be regenerated offline, unchanged, without the browser.

% ---------------------------------------------------------------------------
\section{Conclusion}
\label{sec:conclusion}

We have described STEMKit, a suite of 21 browser-based tools for computational
chemistry built on a tested, dependency-injected JavaScript core. The
architecture addresses three constraints simultaneously that existing tooling
addresses only in pairs: it requires no installation, transmits no data, and
remains scriptable.

The privacy property is structural rather than contractual. Because computation
occurs entirely within the browser, there is no server to receive data and
consequently no policy to trust. For researchers handling unpublished results
or material under confidentiality agreement, this distinction is the difference
between a usable tool and an unusable one.

The reproducibility property follows from the separation of computation from
presentation. The identical modules that execute behind the browser interface
execute under Node.js, so an analysis explored interactively may be captured as
a script and version-pinned without rewriting.

The defects found during extraction were the most useful outcome of this work.
All three had survived in software that ran without error and produced
plausible numbers. None would have been caught by testing the code against our
own expectations of it; each surfaced only when the results were compared with
SciPy and NumPy. A \SI{15}{\percent} error in a reported skewness is not
visible by inspection. Nor is a $p$-value floored at zero, which looks like a
very strong result. We would encourage other authors of scientific software to
check their numerics against an independent implementation.

% ---------------------------------------------------------------------------
\section*{Data and Code Availability}

Source code, the complete test suite, and documentation are available at
\url{https://github.com/LD-Shell/stemkit} under the MIT licence. The browser
tools are hosted at \url{https://stemkit.net}.

\section*{Conflicts of Interest}

The author declares no competing financial or non-financial interests.

\section*{Acknowledgements}

We thank the maintainers of jStat, Papa Parse, regression.js, Plotly, KaTeX,
and 3Dmol.js, whose libraries STEMKit builds upon.

% ---------------------------------------------------------------------------
\begin{thebibliography}{99}

\bibitem{abraham2015}
M.~J. Abraham, T.~Murtola, R.~Schulz, S.~P\'{a}ll, J.~C. Smith, B.~Hess, and
E.~Lindahl,
\newblock GROMACS: High performance molecular simulations through multi-level
  parallelism from laptops to supercomputers,
\newblock \emph{SoftwareX} \textbf{1--2}, 19--25 (2015).
\newblock \url{https://doi.org/10.1016/j.softx.2015.06.001}

\bibitem{thompson2022}
A.~P. Thompson, H.~M. Aktulga, R.~Berger, D.~S. Bolintineanu, W.~M. Brown,
P.~S. Crozier, P.~J. in~'t~Veld, A.~Kohlmeyer, S.~G. Moore, T.~D. Nguyen,
R.~Shan, M.~J. Stevens, J.~Tranchida, C.~Trott, and S.~J. Plimpton,
\newblock LAMMPS --- a flexible simulation tool for particle-based materials
  modeling at the atomic, meso, and continuum scales,
\newblock \emph{Comput. Phys. Commun.} \textbf{271}, 108171 (2022).
\newblock \url{https://doi.org/10.1016/j.cpc.2021.108171}

\bibitem{tribello2014}
G.~A. Tribello, M.~Bonomi, D.~Branduardi, C.~Camilloni, and G.~Bussi,
\newblock PLUMED 2: New feathers for an old bird,
\newblock \emph{Comput. Phys. Commun.} \textbf{185}(2), 604--613 (2014).
\newblock \url{https://doi.org/10.1016/j.cpc.2013.09.018}

\bibitem{michaudagrawal2011}
N.~Michaud-Agrawal, E.~J. Denning, T.~B. Woolf, and O.~Beckstein,
\newblock MDAnalysis: A toolkit for the analysis of molecular dynamics
  simulations,
\newblock \emph{J. Comput. Chem.} \textbf{32}(10), 2319--2327 (2011).
\newblock \url{https://doi.org/10.1002/jcc.21787}

\bibitem{virtanen2020}
P.~Virtanen, R.~Gommers, T.~E. Oliphant, M.~Haberland, T.~Reddy,
D.~Cournapeau, \emph{et al.},
\newblock SciPy 1.0: fundamental algorithms for scientific computing in Python,
\newblock \emph{Nat. Methods} \textbf{17}(3), 261--272 (2020).
\newblock \url{https://doi.org/10.1038/s41592-019-0686-2}

\bibitem{harris2020}
C.~R. Harris, K.~J. Millman, S.~J. van~der~Walt, R.~Gommers, P.~Virtanen,
D.~Cournapeau, \emph{et al.},
\newblock Array programming with NumPy,
\newblock \emph{Nature} \textbf{585}(7825), 357--362 (2020).
\newblock \url{https://doi.org/10.1038/s41586-020-2649-2}

\bibitem{tiesinga2021}
E.~Tiesinga, P.~J. Mohr, D.~B. Newell, and B.~N. Taylor,
\newblock CODATA recommended values of the fundamental physical constants: 2018,
\newblock \emph{Rev. Mod. Phys.} \textbf{93}(2), 025010 (2021).
\newblock \url{https://doi.org/10.1103/RevModPhys.93.025010}

\bibitem{welch1947}
B.~L. Welch,
\newblock The generalization of `Student's' problem when several different
  population variances are involved,
\newblock \emph{Biometrika} \textbf{34}(1--2), 28--35 (1947).
\newblock \url{https://doi.org/10.1093/biomet/34.1-2.28}

\bibitem{dagostino1971}
R.~B. D'Agostino,
\newblock An omnibus test of normality for moderate and large size samples,
\newblock \emph{Biometrika} \textbf{58}(2), 341--348 (1971).
\newblock \url{https://doi.org/10.1093/biomet/58.2.341}

\bibitem{brown1974}
M.~B. Brown and A.~B. Forsythe,
\newblock Robust tests for the equality of variances,
\newblock \emph{J. Am. Stat. Assoc.} \textbf{69}(346), 364--367 (1974).
\newblock \url{https://doi.org/10.1080/01621459.1974.10482955}

\bibitem{holm1979}
S.~Holm,
\newblock A simple sequentially rejective multiple test procedure,
\newblock \emph{Scand. J. Stat.} \textbf{6}(2), 65--70 (1979).

\bibitem{iglewicz1993}
B.~Iglewicz and D.~C. Hoaglin,
\newblock \emph{How to Detect and Handle Outliers},
\newblock ASQC Quality Press, Milwaukee, WI (1993).

\bibitem{grubbs1969}
F.~E. Grubbs,
\newblock Procedures for detecting outlying observations in samples,
\newblock \emph{Technometrics} \textbf{11}(1), 1--21 (1969).
\newblock \url{https://doi.org/10.1080/00401706.1969.10490657}

\bibitem{press2007}
W.~H. Press, S.~A. Teukolsky, W.~T. Vetterling, and B.~P. Flannery,
\newblock \emph{Numerical Recipes: The Art of Scientific Computing},
\newblock 3rd ed., Cambridge University Press, Cambridge (2007).

\end{thebibliography}

\end{document}
